From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-05-01 article/article.tex
ecoli_ppi

 \item \textbf{Arabidopsis protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}

@@

% \begin{figure*}
%      \centering
%     \begin{subfigure}[b]{0.48\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{images/eu_roc_scores.eps}
%         \caption{EU email departments}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.48\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{images/yeast_ppi_roc_scores.eps}
%         \caption{Yeast PPI protein complexes}
%     \end{subfigure}
%     \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
%     Dashed line indicates an AUC score of 0.5 (random chance).
%     Communities are ordered by size.
%     Error bars indicate standard deviation.
%     }
%     \label{fig:real_network_results}
% \end{figure*}
% 
% 
% \begin{figure*}
%     \centering
%     \begin{subfigure}[b]{0.48\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{images/eu_email_nodewise_roc.eps}
%         \caption{EU email departments (986 nodes)}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.48\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{images/yeast_ppi_nodewise_roc.eps}
%         \caption{Yeast PPI protein complexes (1628 nodes)}
%     \end{subfigure}
%     \caption{Receiver Operator Characteristic curves for node communities.
%     Dashed line indicates an AUC score of 0.5 (random chance).
%     Represents mean, shaded area indicates standard deviation.
%     }
%     \label{fig:real_network_nodwise_classifiers}
% \end{figure*}

\subsubsection{High quality labels}
We tested the method on each real network described in section \ref{sec:real_network_descs}.
Figure \ref{fig:real_network_results} shows the mean ROC scores for each community in the relevant networks, organised by size of community at increasing numbers levels of query seed nodes.
On the EU emails and Yeast PPI dataasets, for all communities tested with 3 or more nodes, mean AUC scores calculated with the cross validation method described in section \ref{sec:cross_validation} were above 0.6.
There appeared to be no statistically significant improvements to using more than 3 seed nodes.

The classification for individual nodes is presented in Figure \ref{fig:real_network_nodwise_classifiers}.
Here, binary classification is performed on each node for which community data is available.
The $mu_i({i})$ score is used as a binary classifier.
For the EU email and Yeast PPI the average ROC AUC score to classify node membership inside communities is 0.9 and 0.93, respectively.

>>>>

 \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}

 \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI)}

@@

\begin{figure*}
     \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/eu_email.png}
        \caption{EU email departments}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/yeast_ppi.png}
        \caption{Yeast PPI protein complexes}
    \end{subfigure}

    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi.png}
        \caption{Arabidopsis PPI protein complexes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_go_complexes.png}
        \caption{E coli PPI protein complexes}
    \end{subfigure}
    \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_network_descs}. 
    Results represent the averages over all label sets.
    Shaded areas indicate standard deviations.}
    \label{fig:quality_label_rocs}
\end{figure*}
% 
% 
\subsubsection{High quality labels}
In this section we observe the performance of our method on the real networks described in Section \ref{sec:real_network_descs} with high quality, gold standard, curated labels.
For the EU Emails dataset, the communities relate to real departments of individuals.
For the protein interaction datasets we used manually curated interaction sets.
In the case of the Yeast this was taken from experimentally validated complexes  \cite{pu2008up}.
For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{}.
For the Arabidopsis dataset, the complex sources were more limited.
Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{}.

The results with varying number of seed nodes, for the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
These results represent ROC and AUC statistics
